---
title: "Radiomic Nomogram Construction"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction
Generating Radiomic Signature the differential diagnosis of breast masses.

Initial Setup and Package Loads in R 

Packages used for the analysis.
```{r initial_setup, cache=FALSE, message = FALSE, warning = FALSE}
library(glmnet);library(rms);library(pROC);library(corrplot);library(ggplot2);library(DMwR);library(mRMRe);library(caret);library(corrplot);library(RColorBrewer);library(ICC);library(DTComPair);library(knitr);library(tidyverse)

## Global options

options(max.print="75")
opts_chunk$set(comment=NA,
               message=FALSE,
               warning=FALSE)
opts_knit$set(width=75)

skimr::skim_with(numeric = list(hist = NULL),
                 integer = list(hist = NULL))

```

# Loading the Raw Data into R 
```{r}
dfRadiomicsFeature_bmus <- read.csv("./sample/sample_bmus.csv", header=T, sep=',')
dfRadiomicsFeature_es <- read.csv("./sample/sample_es.csv", header=T, sep=',')
dfClinicalFeature <- read.csv("./sample/sample_clinical.csv", header=T, sep=',')
print("Input data dimension of bmus:")
print(dim(dfRadiomicsFeature_bmus))
print("Input data dimension of es:")
print(dim(dfRadiomicsFeature_es))
print("Input data dimension of clinical:")
print(dim(dfClinicalFeature))
head(dfClinicalFeature)
dfPredict <- dfClinicalFeature[c("ID", "Label")]
```

# Construct Radiomics Signature based on bmus
```{r}
objRadiomics <- read.csv("./model/objRadiomics_bmus.csv", header=T, sep=',', stringsAsFactors = F)
objRadiomics
objScale <- read.csv("./model/objCenterScale_bmus.csv", header=T, sep=',', stringsAsFactors = F)
useRadiomicsFeatureNames <- objRadiomics[["y"]][2:nrow(objRadiomics)]
dfInput = dfRadiomicsFeature_bmus[useRadiomicsFeatureNames]
for (featureName in useRadiomicsFeatureNames) {
      dfInput[[featureName]] <- (dfInput[[featureName]]-objScale[[featureName]][1]) / objScale[[featureName]][2]
}

tmpRes <- lapply(2:nrow(objRadiomics), function(i) {
    featureValues <- dfInput[[objRadiomics[["y"]][i]]]
    tmpValues <- featureValues*objRadiomics[["x"]][i]
    dfValues <- data.frame(tmpValues)
})
tmpStore <- data.frame(tmpRes)
tmpStore[[objRadiomics[["y"]][1]]] <- rep(objRadiomics[["x"]][1], nrow(tmpStore))
Signature_bmus <- rowSums(tmpStore)
dfPredict[["Signature_bmus"]] = Signature_bmus
dfPredict
# show predict signature values
threshold_bmus <- -0.619444282
dfShowSet <- subset(dfPredict, select = c("Label", "Signature_bmus"))
dfShowSetOrder <- dfShowSet[order(dfShowSet[["Signature_bmus"]]),]
dfShowSetOrder<-within(dfShowSetOrder,{
  color<-NA
  color[dfShowSetOrder[["Label"]] == 0]<-"red"
  color[dfShowSetOrder[["Label"]] == 1]<-"green"})
barplotTitle <- sprintf("Radiomics signature for each patient by bmus")
dev.new()
barplot((dfShowSetOrder[["Signature_bmus"]]-threshold_bmus),
        col=dfShowSetOrder$color,
        border = NA,
        space = 0,
        main="Radiomics signature for each patient by bmus",
        ylab="Radiomics signature",
        ylim=c(-5, 5))
legend("bottomright",
       legend=c("LowRisk", "HighRisk"),
       pch=15,col=c("red", "green"))
```


# Construct Radiomics Signature based on es
```{r}
# rm(objRadiomics)
# rm(objScale)
# rm(useRadiomicsFeatureNames)
# rm(dfInput)
# rm(tmpRes)
# rm(tmpStore)
# rm(threshold_bmus)
objRadiomics <- read.csv("./model/objRadiomics_es.csv", header=T, sep=',', stringsAsFactors = F)
objRadiomics
objScale <- read.csv("./model/objCenterScale_es.csv", header=T, sep=',', stringsAsFactors = F)
useRadiomicsFeatureNames <- objRadiomics[["y"]][2:nrow(objRadiomics)]
dfInput = dfRadiomicsFeature_es[useRadiomicsFeatureNames]
for (featureName in useRadiomicsFeatureNames) {
      dfInput[[featureName]] <- (dfInput[[featureName]]-objScale[[featureName]][1]) / objScale[[featureName]][2]
}

tmpRes <- lapply(2:nrow(objRadiomics), function(i) {
    featureValues <- dfInput[[objRadiomics[["y"]][i]]]
    tmpValues <- featureValues*objRadiomics[["x"]][i]
    dfValues <- data.frame(tmpValues)
})
tmpStore <- data.frame(tmpRes)
tmpStore[[objRadiomics[["y"]][1]]] <- rep(objRadiomics[["x"]][1], nrow(tmpStore))
Signature_es <- rowSums(tmpStore)
dfPredict[["Signature_es"]] = Signature_es
dfPredict
# show predict signature values
threshold_es <- -0.6621125775
dfShowSet <- subset(dfPredict, select = c("Label", "Signature_es"))
dfShowSetOrder <- dfShowSet[order(dfShowSet[["Signature_es"]]),]
dfShowSetOrder<-within(dfShowSetOrder,{
  color<-NA
  color[dfShowSetOrder[["Label"]] == 0]<-"red"
  color[dfShowSetOrder[["Label"]] == 1]<-"green"})
barplotTitle <- sprintf("Radiomics signature for each patient by bmus")
dev.new()
barplot((dfShowSetOrder[["Signature_es"]]-threshold_es),
        col=dfShowSetOrder$color,
        border = NA,
        space = 0,
        main="Radiomics signature for each patient by es",
        ylab="Radiomics signature",
        ylim=c(-5, 5))
legend("bottomright",
       legend=c("LowRisk", "HighRisk"),
       pch=15,col=c("red", "green"))
```

# Construct Clinical Risk based on clinical factors
```{r}
# rm(objRadiomics)
# rm(objScale)
# rm(useRadiomicsFeatureNames)
# rm(dfInput)
# rm(tmpRes)
# rm(tmpStore)
# rm(threshold_es)

objClinical <- read.csv("./model/objClinical.csv", header=T, sep=',', stringsAsFactors = F)
objClinical

dfInput = dfClinicalFeature
tmpRes <- lapply(2:nrow(objClinical), function(i) {
    featureValues <- dfInput[[objClinical[["Variable"]][i]]]
    tmpValues <- featureValues*objClinical[["Coefficient"]][i]
    dfValues <- data.frame(tmpValues)
})
tmpStore <- data.frame(tmpRes)
tmpStore[[objClinical[["Variable"]][1]]] <- rep(objClinical[["Coefficient"]][1], nrow(tmpStore))
RiskLog_Clinical <- rowSums(tmpStore)
# dfPredict[["RiskLog_clinical"]] = RiskLog_clinical
dfPredict[["Risk_Clinical"]] = plogis(RiskLog_Clinical)
dfPredict

# show predict values
threshold_clinical <- 0.436346787004995
dfShowSet <- subset(dfPredict, select = c("Label", "Risk_Clinical"))
dfShowSetOrder <- dfShowSet[order(dfShowSet[["Risk_Clinical"]]),]
dfShowSetOrder<-within(dfShowSetOrder,{
  color<-NA
  color[dfShowSetOrder[["Label"]] == 0]<-"red"
  color[dfShowSetOrder[["Label"]] == 1]<-"green"})
barplotTitle <- sprintf("Clinical Risk for each patient")
dev.new()
barplot((dfShowSetOrder[["Risk_Clinical"]]-threshold_clinical),
        col=dfShowSetOrder$color,
        border = NA,
        space = 0,
        main="Clinical Risk for each patient",
        ylab="Probability Risk",
        ylim=c(-1, 1))
legend("bottomright",
       legend=c("LowRisk", "HighRisk"),
       pch=15,col=c("red", "green"))
```


# Construct Radiomics Nomogram based on radiomics signature and clinical factors
```{r}
# rm(dfInput)
# rm(tmpRes)
# rm(tmpStore)
objRadiomicsNomogram <- read.csv("./model/objRadiomicsNomogram.csv", header=T, sep=',', stringsAsFactors = F)
objRadiomicsNomogram

dfInput = cbind(dfClinicalFeature, dfPredict[c("Signature_bmus", "Signature_es")])
tmpRes <- lapply(2:nrow(objRadiomicsNomogram), function(i) {
    featureValues <- dfInput[[objRadiomicsNomogram[["Variable"]][i]]]
    tmpValues <- featureValues*objRadiomicsNomogram[["Coefficient"]][i]
    dfValues <- data.frame(tmpValues)
})
tmpStore <- data.frame(tmpRes)
tmpStore[[objRadiomicsNomogram[["Variable"]][1]]] <- rep(objRadiomicsNomogram[["Coefficient"]][1], nrow(tmpStore))
RiskLog_RadiomicsNomogram <- rowSums(tmpStore)
# dfPredict[["RiskLog_RadiomicsNomogram"]] = RiskLog_RadiomicsNomogram
dfPredict[["Risk_RadiomicsNomogram"]] = plogis(RiskLog_RadiomicsNomogram)
dfPredict

# show predict values
threshold_nomo <- 0.275281806650769
dfShowSet <- subset(dfPredict, select = c("Label", "Risk_RadiomicsNomogram"))
dfShowSetOrder <- dfShowSet[order(dfShowSet[["Risk_RadiomicsNomogram"]]),]
dfShowSetOrder<-within(dfShowSetOrder,{
  color<-NA
  color[dfShowSetOrder[["Label"]] == 0]<-"red"
  color[dfShowSetOrder[["Label"]] == 1]<-"green"})
barplotTitle <- sprintf("Risk of Radiomics Nomogram for each patient")
dev.new()
barplot((dfShowSetOrder[["Risk_RadiomicsNomogram"]]-threshold_nomo),
        col=dfShowSetOrder$color,
        border = NA,
        space = 0,
        main="Risk of Radiomics Nomogram for each patient",
        ylab="Probability Risk",
        ylim=c(-1, 1))
legend("bottomright",
       legend=c("LowRisk", "HighRisk"),
       pch=15,col=c("red", "green"))

```

# Show the performance of different models
```{r}
dfInput <- dfPredict
dfInput
write.csv(dfPredict, "./sample result/result.csv", row.names = FALSE)
# plotColors <- c('yellowgreen', 'lightblue', 'lightcoral', 'lightcyan','yellow', 
#                    'lightgreen',
#                    'yellowgreen', 'darkcyan', 'blue', 'brown',
#                    'chartreuse', 'coral', 'darkgreen', 'lightblue',
#                    'orange', 'orangered', 'purple', 'red')
plotColors <- c('yellowgreen', 'lightblue', 'lightcoral', "orange", 'red')
showFeatureNames <- c("Signature_bmus", "Signature_es", "Risk_Clinical", "Risk_RadiomicsNomogram")
# showFeatureNames <- c("Signature_bmus", "Signature_bmus", "Signature_bmus", "Risk_RadiomicsNomogram")
for (indexFeature in 1:4){
  rocFeature <- roc(
    response=dfInput[["Label"]], 
    predictor=dfInput[[showFeatureNames[indexFeature]]]) 
  if (1 == indexFeature) {
    plot(rocFeature, 
         col=plotColors[indexFeature], main = "ROC of different models", lwd=3) 
  } else {
    plot.roc(rocFeature, add=TRUE, col=plotColors[indexFeature], lwd=3)
  }
}
legend("bottomright", 
       legend=showFeatureNames,
       col=plotColors[1:4],
       lty=1,lwd=2,bty='n')

```
